Crossing Origins by Crossing Formats

### 2012-11-29 main.tex
intro

General introduction for web application security.

The following attacks have been particularly successful (support with
references).

\subsection{Injection attacks}

Injection attacks have gone from classical to sophisticated.

New breed of attacks.

\subsection{Content repurposing attacks}

Server side verification

Examples

Bridge to the next section saying that we take these attacks to the next level.

\todo{Define SOP}

@@

By crossing origins we mean being able to request and access content
which is normally restricted under the Same-Origin Policy. 
Recall that SOP dictates that a two document can only access each others 
content and resources if they share the same origin. Similarly this applies to communication as 
well; a document can only directly communicate with the server from which it originated. 
This is not to be confused with Cross-Origin Resource Sharing (CORS), which is an 
intentional relaxing of the SOP.

>>>>

Web application security is concerned with protecting information as
it is manipulated by web applications. The different trust domains
correspond to different Internet origins. A major goal for web
application security is preventing undesired communication across
origins. 
%
With the goal of separating information from the different origins,
today's browsers enforce the \emph{same-origin policy} (SOP). SOP
restricts only allows access between two documents if they share the
origin. In addition, a document can only directly communicate with the
server from which it originates.

There are several classes of cross-domain attacks that circumvent SOP.
The OWASP top 10 list~\cite{OWASP:top10:10} places injection
and \emph{cross-site scripting} (XSS) attacks as two top security
risks for web applications.
%
A classical XSS attack injects a malicious script in the context of a
trusted origin. This opens up opportunities for leaking sensitive
information that users might have in the context of the trusted origin
such as cookies, personal information, and session tokens.

XSS attacks are relatively well understood by researchers and
developers~\cite{XSS:understood}. Known defense include various
flavors of \emph{sanitization} on server side and the
\emph{content security policy} (CSP) on client side. Sanitization
is often performed by the server which sanitizes input data
before it is used in the generated web pages. Content security policy puts
requirement on the structure of the document and the origins of the
scripts that are included by web pages.

This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
The existing defense mechanisms fall short to prevent these attacks
from achieving cross-domain communication.

A polyglot is a program that is valid in multiple programming languages. Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. We perform a systematic study of
PDF-based injection and content repurposing attacks. We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (such as PDF readers) show how to mitigate the attacks.

\todo{Emphasize novel attack vectors}

\emph{Injection attacks} are becoming increasingly more sophisticated by
operating across multiple languages. \emph{Content repurposing} attacks supply
malicious payload that appears formatted as benign content.

The paper is organized as follows...

@@

By crossing origins we mean being able to request and access content
which is normally restricted under the Same-Origin Policy. 
Recall that SOP dictates that a two document can only access each others 
content and resources if they share the same origin. Similarly this applies to communication as 
well; a document can only directly communicate with the server from which it originated. 
This is not to be confused with Cross-Origin Resource Sharing (CORS)~\cite{CORS}, which is an 
intentional relaxing of the SOP.
